systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-07-02 paper/trunk/JSS/response_A.tex

% 
%     It would also be nice to have some more control about the amount of output of
%     the summary() method. Currently, the output can become very long easily when the
%     number of equations increases. One could want to control the equations and
%     correlations used, e.g., by something like
%       summary(sfobject, equation = ..., cor = ...)
The user has more control about the amount of output of
\code{summary()} now.
We have added arguments \code{residCov} and \code{equations}
to function \code{print.summary.systemfit()}.
Argument \code{residCov} indicates
whether the residual correlation matrix,
the residual covariance matrix, and its determinant are printed;
argument \code{equations} indicates
whether summary results of each equation are printed
(or if just the coefficients are printed).
As users often use \code{summary()} without \code{print()},
we have added arguments \code{printResidCov} and \code{printEquations}
to \code{summary()},
which set default values for arguments \code{residCov} and \code{equations}
of function \code{print.summary.systemfit()}.

% 
%
\subsection{Computations in systemfit}
%   o computations in systemfit()
% 
%     A few computations within the systemfit() functions can be further streamlined.
%     A simple modification is to use
%       method %in% c("OLS", "WLS", ...)
%     instead of
%       method == "OLS" | method == "WLS" | method == ...
We have streamlined the source code of the \pkg{systemfit} package.
For instance, we have followed the suggestion of this referee
and replaced all
°\code{method == "OLS" | method == "WLS" | method == ...}°
by °\code{method \%in\% c("OLS", "WLS", ...)}°.

%     Furthermore, various marix computations can be made even more stable. Currently,
%     the code still has    
%       solve(crossprod(X), crossprod(X,Y))    
%       solve(crossprod(X))
%     which looks very similar to the code presented in Bates (2004). However, Bates
%     (2004) uses the "Matrix" package, which has specialized solve() for certain
%     matrix types. To perform this `by hand' without Matrix, one way would be re-using
%     lm.fit() for the first command. Alternatively, the QR or Cholesky decomposition
%     could be carried out using qr() or chol(). The latter command could be replaced
%     by
%      chol2inv(qr.R(qr(X)))
%      chol2inv(chol(crossprod(X)))
%     where chol() should be faster but qr() might be more accurate.
%
\subsection{Replication of Textbook Results (5)}
%   o Replication of textbook results (5)
% 
%     Having a section like this is excellent and should help teachers and students
%     for using systemfit in their lectures. Furthermore, it encourages reproducible
%     research which always deserves support. However, I would suggest to streamline
%     the section to make it more readable. The section should discuss its aims (where
%     I would add replication to reliability) and summarize the most important results
%     and experiences from the replication.
As suggested by this referee,
we have added the aims °teaching° and °reproducible research°
to further motivate this section.
As this section no longer focusses exclusively on testing reliability,
we have renamed it to °Replication of textbook results°.

%     Then, I would pick a `typical' example and
%     discuss it in some more detail with full R output. For the remaining examples,
%     the input suffices as long as there are no deviations of the systemfit results
%     from the published numbers.
To make this section more readable, we have removed the estimation results
and present the commands to replicate these results only.

% 
%     In addition to Table 14.1 and 14.2, I tried to replicate Table 14.3 with
%     ML estimates (using iterated FGLS) in Greene (2003) via 
%       systemfitClassic("WSUR", invest ~ value + capital, "firm", "year",
%                        data = GrunfeldGreene, rcovformula = 0, pooled = TRUE, maxiter = 1000)    
%     for the pooled model which yielded rather similar results; and via
%       systemfitClassic("SUR", invest ~ value + capital, "firm", "year",
%                        data = GrunfeldGreene, rcovformula = 0, maxiter = 1000)    
%     for the full model which is not unsimilar to Greene's results but also not very
%     close either. Is this a problem of systemfit or of Greene or of me fitting the
%     wrong model?
% 
%     Having two Grunfeld data sets is confusing as the data used by Theil is simply
%     a subset of the data used by Greene:
%       subset(GrunfeldGreene, firm %in% c("General Electric", "Westinghouse"))
%     Of course, there are different versions of this data set, but neither the paper
%     nor the manual pages of GrunfeldGreene and GrunfeldTheil appropriately discuss
%     the problem. From the manual and the paper, the reader is only able to feel
%     vaguely insecure about the appropriateness of the selected subsets. Also note
%     that a more complete (and slightly different) version of the data set is
%     available in package "Ecdat".
The data set \code{GrunfeldTheil} has been removed,
because it is a subset of the data set \code{GrunfeldGreene}.
We have improved the discussion of different versions of Grunfeld's data set
in the documentation of \code{GrunfeldGreene}
and we have added this discussion in the paper.
Furthermore, we have added a note
that a correct version of this data set with five additional firms
is available as data set \code{Grunfeld} in the \pkg{Ecdat} package.

### 2007-07-02 paper/trunk/JSS/response_A.tex

%     Furthermore, various marix computations can be made even more stable. Currently,
%     the code still has    
%       solve(crossprod(X), crossprod(X,Y))    
%       solve(crossprod(X))
%     which looks very similar to the code presented in Bates (2004). However, Bates
%     (2004) uses the "Matrix" package, which has specialized solve() for certain
%     matrix types. To perform this `by hand' without Matrix, one way would be re-using
%     lm.fit() for the first command. Alternatively, the QR or Cholesky decomposition
%     could be carried out using qr() or chol(). The latter command could be replaced
%     by
%      chol2inv(qr.R(qr(X)))
%      chol2inv(chol(crossprod(X)))
%     where chol() should be faster but qr() might be more accurate.
%
\subsection{Replication of Textbook Results (5)}
%   o Replication of textbook results (5)
% 
%     Having a section like this is excellent and should help teachers and students
%     for using systemfit in their lectures. Furthermore, it encourages reproducible
%     research which always deserves support. However, I would suggest to streamline
%     the section to make it more readable. The section should discuss its aims (where
%     I would add replication to reliability) and summarize the most important results
%     and experiences from the replication.
As suggested by this referee,
we have added the aims °teaching° and °reproducible research°
to further motivate this section.
As this section no longer focusses exclusively on testing reliability,
we have renamed it to °Replication of textbook results°.

%     Then, I would pick a `typical' example and
%     discuss it in some more detail with full R output. For the remaining examples,
%     the input suffices as long as there are no deviations of the systemfit results
%     from the published numbers.
To make this section more readable, we have removed the estimation results
and present the commands to replicate these results only.

% 
%     In addition to Table 14.1 and 14.2, I tried to replicate Table 14.3 with
%     ML estimates (using iterated FGLS) in Greene (2003) via 
%       systemfitClassic("WSUR", invest ~ value + capital, "firm", "year",
%                        data = GrunfeldGreene, rcovformula = 0, pooled = TRUE, maxiter = 1000)    
%     for the pooled model which yielded rather similar results; and via
%       systemfitClassic("SUR", invest ~ value + capital, "firm", "year",
%                        data = GrunfeldGreene, rcovformula = 0, maxiter = 1000)    
%     for the full model which is not unsimilar to Greene's results but also not very
%     close either. Is this a problem of systemfit or of Greene or of me fitting the
%     wrong model?
In theory, iterated FGLS should converge to ML results,
but in practice these results often (more or less) slightly deviate.
As the \pkg{systemfit} package currently does not provide ML estimations,
we cannot determine the reason for the deviations
between \code{systemfit()}'s iterated FGLS results
and Greene's ML results.
We will take a look at this issue,
when we have finished to implement ML estimations in \pkg{systemfit()}.

% 
%     Having two Grunfeld data sets is confusing as the data used by Theil is simply
%     a subset of the data used by Greene:
%       subset(GrunfeldGreene, firm %in% c("General Electric", "Westinghouse"))
%     Of course, there are different versions of this data set, but neither the paper
%     nor the manual pages of GrunfeldGreene and GrunfeldTheil appropriately discuss
%     the problem. From the manual and the paper, the reader is only able to feel
%     vaguely insecure about the appropriateness of the selected subsets. Also note
%     that a more complete (and slightly different) version of the data set is
%     available in package "Ecdat".
The data set \code{GrunfeldTheil} has been removed,
because it is a subset of the data set \code{GrunfeldGreene}.
We have improved the discussion of different versions of Grunfeld's data set
in the documentation of \code{GrunfeldGreene}
and we have added this discussion in the paper.
Furthermore, we have added a note
that a correct version of this data set with five additional firms
is available as data set \code{Grunfeld} in the \pkg{Ecdat} package.
